Reproducible Summary Tables with gtsummary

### 2020-12-10 RJtemplate_gtsummary_submission.tex
Updates from Overleaf

% !TeX root = RJwrapper.tex
\title{Reproducible Summary Tables with gtsummary}
\author{by Daniel D. Sjoberg, Karissa Whiting, Margie Hannum, Michael Curry}

@@

@@

@@

@@

survfit(Surv(ttdeath, death) ~ trt, trial) %>%
  tbl_survfit(times = c(12, 24),
              label_header = "**{time} Month**") %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[height=4cm]{survfit.png}
  \centering
\end{figure}

@@

\address{Author One\\
  Affiliation\\
  Address\\
  Country\\
  (ORCiD if desired)\\
  \email{author1@work}}

\address{Author Two\\
  Affiliation\\
  Address\\
  Country\\
  (ORCiD if desired)\\
  \email{author2@work}}

\address{Author Three\\
  Affiliation\\
  Address\\
  Country\\
  (ORCiD if desired)\\
  \email{author3@work}}

>>>>

% !TeX root = RJwrapper.tex
\title{Reproducible Summary Tables with gtsummary}
\author{by Daniel D. Sjoberg, Karissa Whiting, Michael Curry}

@@

To show use of gtsummary functions, we will use a simulated clinical trial data set containing baseline characteristics of 200 patients who received Drug A or Drug B as well as the outcome of tumor response to the treatment.
Each variable in the data frame has been assigned an attribute label (i.e. \texttt{attr(trial\$trt, "label") == "Chemotherapy Treatment"}) with the labelled[add ref] package. 
These labels are displayed in the {gtsummary} tables by default. Using {gtsummary} on a data frame without labels will print variable names in place of variable labels with the option to update the text displayed.

@@

The default output from \texttt{tbl\_summary()} is meant to be publication ready.
The \texttt{tbl\_summary()} function can take, at minimum, a data frame as the only input, and returns descriptive statistics for each column in the data frame.
This is often the first table of clinical manuscripts and describes characteristics of the cohort under study.
A simple example is shown below.
Notably, by specifying the \texttt{by=} argument, you can stratify the summary table. 
In the example below, we have split the table by the treatment a patient received.

@@

Note the sensible defaults with this basic usage.

\begin{itemize}
\item Variable types are automatically detected so that appropriate descriptive statistics are calculated.
\item Label attributes from the data set are automatically printed.
\item Missing values are listed as “Unknown” in the table.
\item Variable levels are indented and footnotes are added.
\end{itemize}

Each of the defaults may be customized using the \texttt{tbl\_summary()} function arguments.

@@

survfit(Surv(ttdeath, death) ~ trt, trial) %>%
  tbl_survfit(times = c(12, 24),
              label_header = "**{time} Month**") %>%
  add_p()
\end{example}

% TODO: I do not understand why this isn't being placed below the code! https://www.overleaf.com/learn/latex/Positioning_of_Figures
\begin{figure}[h!]
  \includegraphics[height=4cm]{survfit.png}
  \centering
\end{figure}

@@

\address{Daniel D. Sjoberg\\
  Memorial Sloan Kettering Cancer Center\\
  1275 York Ave., New York, New York 10022\\
  USA\\
  ORCID 0000-0003-0862-2018\\
  \email{sjobergd@mskcc.org}}

\address{Karissa Whiting\\
  Memorial Sloan Kettering Cancer Center\\
  1275 York Ave., New York, New York 10022\\
  USA\\
  ORCID 0000-0002-4683-1868\\
  \email{author2@work}}

\address{Michael Curry\\
  Memorial Sloan Kettering Cancer Center\\
  1275 York Ave., New York, New York 10022\\
  USA\\
  ORCID 0000-0002-0261-4044\\
  \email{author3@work}}
